Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-29 paper/paper.Rmd
Revise intro; removed osf from table

header-includes:
   - \usepackage{lscape}
   - \usepackage{multicol}

@@

In the current article, we address the practical barriers of completing replications as part of required coursework and discuss the methodological decisions that replication projects must address more broadly. Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course. Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work. But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly. Even in these cases, however, replication research of the type we conduct here contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.

@@

\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\ 
  \hline
Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects. All project materials available publicly at osf.io/98ta4/files/. * marks projects where the number of trials was modified.} 
\label{tab:summary}
\end{table}

@@

@@

<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->

>>>>

header-includes:
   - \usepackage{pdflscape}
   - \usepackage{multicol}

@@

In the current article, we address the practical barriers of completing replications as part of required coursework and discuss the methodological decisions that such replication projects must address more broadly. Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course. Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings. We consider a number of criteria for evaluating replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures suggest that replications performed in the classroom are representative of larger, more systematic efforts. Perhaps more importantly, these results provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in their own future work. 
<!-- But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly. Even in these cases, however, replication research of the type we conduct here contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings. -->

@@

\specialcell{Citation\\(Psychological Science; 2015)} & Expt. & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity}\\ 
  \hline
Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & \\ 
Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 &\\ 
Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 &\\ 
Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 &\\ 
Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67&\\ 
Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67& \\ 
Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33& \\ 
Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00& \\ 
Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33&\\ 
Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00& \\ 
Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00&\\ 
   \hline
\end{tabular}
\caption{\label{tab:summary} Summary characteristics of original studies and our replications. All project materials available publicly at osf.io/98ta4/files/, and links to individual project preregistrations, reports, and web experiments are available at osf.io/98ta4/wiki/ * marks projects where the number of trials was modified.} 
\label{tab:summary}
\end{table}

@@

\begin{center}
\begin{landscape}

@@

\end{landscape}
\end{center}
<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->
